\cvsection{Projects}
\begin{cventries}
  \cventry
    {Php, Bootstrap4 \& MySql}
    {E-Election}
    {A Online Election Portal}
    {Jan. 2016 - Dec 2016}
    {
      \begin{cvitems}
        \item {Developed an easy and free to use Election portal for college students.}
        \item {Useful during Annual Council Elections for various posts such as Class, Music, Sport, Sort, E-cell Inchage.}
      \end{cvitems}
    }
  \cventry
    {Python, IoT, Machine Learning \& Face Recognition}
    {Smart Rakshak}
    {A smart Home Secuirty solution}
    {Aug. 2017 - Mar. 2018}
    {
      \begin{cvitems}
        \item {Developed an Economic and Effective Security solution for homes.}
        \item{Build with the help of latest technologies like IoT and Machine learning for Face recognition.}
        \item{After a motion detection there will be a face verification  after which, only authorized personnel will be allowed to enter home else Homeowner will be notified with an SMS and E-mail.}
      \end{cvitems}
    }
     \cventry
    {Python, Bash \& Web Scraping}
    {Intelligent Codemate}
    {A terminal based application}
    {Aug. 2018- Mar. 2019}
    {
      \begin{cvitems}
        \item {Developed a novel approach to improve error solving process by suggesting an optimal solution to the error given by the program.}
        \item{After passing the file to be executed on the terminal then, as per the file type it will be executed.}
        \item{If there is an error in the file, the error will be extracted and will be searched on the internet for the possible solution and the site will be scrapped then, the solution will be displayed on to the terminal itself.}
      \end{cvitems}
    }
     \cventry
    {Java \& Socket Programming}
    {Quick Share}
    {A Command Line File Transfer}
    {Aug. 2017  Dec 2017}
    {
      \begin{cvitems}
        \item {A Command line application to transfer one file from one PC to another connected in the same LAN.}
        \item{Only Source and Destination IP address need to transfer files, simple and quick because no authentication required.}
      \end{cvitems}
    }
    
    \cventry
    {VueJs and Bootstrap}
    {Just Resume}
    {A Dynamic Resume Building tool}
    {Aug. 2019  Dec 2018}
    {
      \begin{cvitems}
        \item {A free Resume building tool to make process more interactive.}
        \item{Features includes Free download and Cloud Storage. }
      \end{cvitems}
    }
\end{cventries}
